Assessing United States county-level exposure for research on tropical cyclones and human health

### 2019-01-27 writing/ehp_discussion.tex
Rearrange content

Distance from a tropical cyclone's track is relatively easy to measure and has
been used as an operational metric of exposure to tropical cyclones in previous
large-scale studies (examples included in Figure S1). Since distance itself
does not constitute a hazard, distance is meant in these cases as a surrogate
to capture exposure to hazards from the tropical cyclone. However, here we
found that in assessing U.S.  county-level exposure to tropical cyclones,
distance is, at best, a moderate, and often a very poor, surrogate for exposure
to the specific tropical cyclone hazards of high wind, extreme rainfall,
flooding, and tornadoes (Figure \ref{fig:jaccard}).  Therefore, use of distance
to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies \citep{savitz2016interpreting, armstrong1998effect}.

In some cases, this exposure misclassification may be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest). For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, since most tropical cyclones
rapidly decrease in sustained windspeed following landfall. However, tropical
cyclone exposures based on distance can extend well inland, following the
tropical cyclone's tracks, but may not adequately capture all wind-exposed
counties near the coast. In this case, if the etiologically-relevant exposure
is high wind but exposure is classified based on distance, the probability of
being misclassified as unexposed would be higher in coastal counties, while the
probability of being misclassified as exposed would be higher in inland
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, differential
exposure misclassification would exist \citep{savitz2016interpreting}. Such
differential exposure misclassification can bias estimates of tropical cyclone
effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists) \citep{savitz2016interpreting,
armstrong1998effect}. The use of a single hazard-based metric (e.g., wind)
could cause similar problems if the impact is driven, at least in part, by a
different hazard or by multiple hazards of the tropical cyclone.

Our findings---that county-level tropical cyclone exposure assessment varies
substantially when different exposure measurements are considered---aligns with
previous research from atmospheric science and related fields on the
characteristics of tropical cyclones. While tropical cyclone rainfall and
windspeed are often well-correlated when the tropical cyclone is over water
\citep{cerveny2000}, this relationship often does not remain as strong once the
hurricane has made landfall \citep{jiang2008}.  Fast-moving tropical cyclones
bring higher risks of dangerous winds inland \citep{kruk2010}, while
slow-moving tropical cyclone are likely to bring more rain
\citep{rappaport2000} and cause more damage because of sustained hazardous
conditions \citep{rezapour2014}. Further, while the likelihood and extent of
flooding during a tropical cyclone is related to the tropical cyclone's
rainfall, it is also driven by factors like top soil saturation and the
structure of the water basin's drainage network \citep{chen2015, rees2001}.
However, we did find a small set of tropical cyclone for which for which
agreement between metrics were unusually high (e.g., Floyd in 1999, Irene in
2011, Hannah in 2008, Bertha in 1996) For this set of tropical cyclones, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In our results, wind-based exposure had a strong coastal pattern, with almost
all exposures in counties within about 200 kilometers (124 miles) of the
coastline. This is consistent with the
dramatic decrease in wind intensity that typically characterizes the landfall
of tropical cyclones. Exposures by rain- and distance-based metrics often extended further inland compared to the wind-based
metric, up to the Appalachian mountains. This agrees with previous research
indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding \citep{rees2001}.  Almost all tornado-based exposures were in
southern coastal states. This pattern echoes
previous findings that most noteworthy tropical cyclone-related tornadoes occur
on the right-side of the tropical cyclone track in Atlantic Basin U.S. storms
\citep{moore2012}.

The tropical cyclone exposure averages shown in Figure
\ref{fig:averageexposure} are limited as estimates of long-term frequencies, as
tropical cyclones follow decadal patterns \citep{kossin2007more} likely not
adequately captured in the available data. However, these frequency maps,
together with evidence from specific tropical cyclones (Figures
\ref{fig:ivanexposure} and \ref{fig:jaccard}),  do illustrate the potential for
strong differences in spatial patterns in tropical cyclone exposures, depending
on which tropical cyclone hazards are considered. A few previous studies have
sought to determine county-level exposure to tropical cyclones over multi-year
periods, including \citet{zandbergen2009}, which estimated exposure in U.S.
counties to all U.S.  landfalling Atlantic basin tropical cyclones between 1851
and 2003, using both a distance-based metric and a metric that combined
distance and windspeed, and \citet{kruk2010}, which explored exposure to
hurricane-related winds in the U.S., including inland areas, for 1900--2008.
Our results suggest that such exposure assessments may perform well in
capturing some tropical cyclone hazards (e.g., wind), but likely miss other
potentially dangerous tropical cyclone exposures, especially for hazards that
repeatedly threaten northern or inland counties (e.g., rain, flooding).

@@

To assist with future tropical cyclone studies, we created and published
open source software to accompany this article \citep{hurricaneexposure,
hurricaneexposuredata}. Many previous studies have used geographical
information system software (e.g., ArcGIS) to assess exposure to tropical
cyclones in the U.S. \citep{grabich2016, zandbergen2009, czajkowski2011,
kruk2010}. Here, we offer methods to map and output historic exposure to
tropical cyclones that does not require the use of proprietary software but
instead uses a package written in the R statistical programming language
\citep{R}, which is free and open-source.

In addition to providing tropical cyclone exposure metrics for individual
hazards, this software and data also allow users to create tropical cyclone
exposure profiles based on multiple hazards or craft exposure indices that
combine hazard metrics \citep{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones
often act synergistically in causing impacts \citep{smith2009}. Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.

In creating this hurricane exposure dataset, we aimed for data that are
reliable, available for all eastern U.S. counties, and have no missing data
within available dates. Further, we have investigated how well these data
correspond with data from other available sources (Figures S7--11). However,
there are still some important limitations. For example, for a few tropical cyclones, 
the model-based wind data might differ from post-storm analysis of wind radii
(e.g., Figure S10), and the re-analysis rainfall data seems to sometime oversmooth
very extreme precipitation (Figure S8). 
The flood and tornado data
came from the National Oceanic and Atmospheric Administration's (NOAA's) Storm
Events database, which, while a widely-used database of events maintained by
NOAA, is based on reports, and so may be prone to underreporting
\citep{Ashley2008flood, Curran2000}, especially in less populated areas
\citep{Witt1998, Ashley2007}, as well as to other reporting errors. While these
are important limitations, we selected these data sources as among the best
currently available for measuring each of these hazards at a multi-county,
multi-year scale.

@@

Previous research has highlighted the range of impacts that tropical cyclones
can have in U.S. communities. However, studies have varied widely in how they assess
exposure to tropical cyclones for exposure, health impact, and other impact
studies, in some cases using distance to the tropical cyclone's track as a
surrogate metric of exposure to a tropical cyclone's hazards. Here we found
large differences in which counties are exposed to different hazards of
tropical cyclones and that distance is, at best, a moderate, and often a very
poor, surrogate for exposure to the specific tropical cyclone hazards of high
wind, extreme rainfall, flooding, and tornadoes. Use of distance as a surrogate
for any of these hazards could lead to exposure misclassification and, in the
case of tropical cyclone risk and impact studies, including epidemiological
studies, result in biased estimates.  Similarly, if such studies disagree on
their findings, it could result from the often poor agreement between exposure
classifications based on these different metrics, making studies that use
different metrics hard to compare or combine in meta-analyses. Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies and basing exposure assessment on measurements of these
hazards. To help with this, we provide extensive tropical cyclone
hazard-related measurements for a large collection of historical Atlantic-basin
cyclones, aggregated at the county level to align with the spatial scale at
which much health-related data is collected.

>>>>

Distance from a tropical cyclone's track is relatively easy to measure and has
been used as an operational metric of exposure to tropical cyclones in previous
large-scale studies (examples include ...). Since distance itself
does not constitute a hazard, distance is meant in these cases as a surrogate
to capture exposure to hazards from the tropical cyclone. However, here we
found that in assessing \ac{US} county-level exposure to tropical cyclones,
distance is, at best, a moderate, and often a very poor, surrogate for exposure
to the specific tropical cyclone hazards of high wind, extreme rainfall,
flooding, and tornadoes (Figure~\ref{fig:jaccard}).  Therefore, use of distance
to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\citep{savitz2016interpreting, armstrong1998effect}.

In some cases, this exposure misclassification may be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest). For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, since most tropical cyclones
rapidly decrease in sustained windspeed following landfall. However, tropical
cyclone exposures based on distance can extend well inland, following the
tropical cyclone's tracks, but may not adequately capture all wind-exposed
counties near the coast. In this case, if the etiologically-relevant exposure
is high wind but exposure is classified based on distance, the probability of
being misclassified as unexposed would be higher in coastal counties, while the
probability of being misclassified as exposed would be higher in inland
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, differential
exposure misclassification would exist~\citep{savitz2016interpreting}. Such
differential exposure misclassification can bias estimates of tropical cyclone
effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\citep{savitz2016interpreting,
armstrong1998effect}. The use of a single hazard-based metric (e.g., wind)
could cause similar problems if the impact is driven, at least in part, by a
different hazard or by multiple hazards of the tropical cyclone.

Our findings\,---\,that county-level tropical cyclone exposure assessment varies
substantially when different exposure measurements are considered\,---\,aligns with
previous research from atmospheric science and related fields on the
characteristics of tropical cyclones. While tropical cyclone rainfall and
windspeed are often well-correlated when the tropical cyclone is over
water~\citep{cerveny2000}, this relationship often does not remain as strong
once the hurricane has made landfall~\citep{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\citep{kruk2010}, while
slow-moving tropical cyclone are likely to bring more
rain~\citep{rappaport2000} and cause more damage because of sustained hazardous
conditions~\citep{rezapour2014}. Further, while the likelihood and extent of
flooding during a tropical cyclone is related to the tropical cyclone's
rainfall, it is also driven by factors like top soil saturation and the
structure of the water basin's drainage network~\citep{chen2015, rees2001}.
However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996) For this set of tropical cyclones, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In our results, wind-based exposure had a strong coastal pattern, with almost
all exposures in counties within about~200~\si{\kilo\metre} (124~mi) of the
coastline. This is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\citep{rees2001}.  Almost all tornado-based exposures were in
southern coastal states. This pattern echoes previous findings that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\citep{moore2012}.

The tropical cyclone exposure averages shown in
Figure~\ref{fig:averageexposure} are limited as estimates of long-term
frequencies, as tropical cyclones follow decadal
patterns~\citep{kossin2007more} likely not adequately captured in the available
data.  However, these frequency maps, together with evidence from specific
tropical cyclones (Figures~\ref{fig:ivanexposure} and~\ref{fig:jaccard}),  do
illustrate the potential for strong differences in spatial patterns in tropical
cyclone exposures, depending on which tropical cyclone hazards are considered.
A few previous studies have sought to determine county-level exposure to
tropical cyclones over multi-year periods, including~\citet{zandbergen2009},
which estimated exposure in \ac{US} counties to all \ac{US} landfalling
Atlantic-basin tropical cyclones between~1851 and~2003, using both a
distance-based metric and a metric that combined distance and windspeed,
and~\citet{kruk2010}, which explored exposure to hurricane-related winds in the
\ac{US}, including inland areas, for~1900\,--\,2008.  Our results suggest that
such exposure assessments may perform well in capturing some tropical cyclone
hazards (e.g., wind), but likely miss other potentially dangerous tropical
cyclone exposures, especially for hazards that repeatedly threaten northern or
inland counties (e.g., rain, flooding).

Dissimilarity in exposure to specific hazards of tropical cyclones can result
in differing patterns in estimates of county-level exposure (Figure~1 [change
to fig. ref]), which can lead to substantial differences in estimates of
population physical exposure (Figure~\ref{fig:topelecdependexposure}), based on
which storm hazard is considered. The measure of a hurricane's intensity, the
Saffir-Simpson scale, expresses intensity as a function of wind speed, and so
fails to capture potential risks from other hazards of the
storm~\citep{smith2009}, and previous assessments of physical exposure to
tropical cyclones have often focused on winds or distance from the storm. For
example, a global study of exposure and vulnerability to natural hazards used a
combination of windspeed above a certain threshold and distance from the
storm's track to assess exposure~\citep{peduzzi2009assessing}. While many storm
impacts might be most strongly linked to wind hazards, there is a growing
recognition of the potential risks of adverse health outcomes and property
damage from rain- and flood-related tropical cyclone hazards in the
\ac{US}~\citep{smith2009}. Such assessments may underemphasize potentially
dangerous exposures to certain regions of the \ac{US}, particularly inland
locations. In fact, based on our assessment of physical exposures to tropical
cyclones among electricity-dependent Medicare beneficiaries, the highest
expected physical exposure under any metric was measured for Philadelphia
County, PA, under the flood metric (Figure~\ref{fig:topelecdependexposure}).
While this county has a similar-sized population of electricity-dependent
Medicare beneficiaries as Miami-Dade County, FL
(Figure~\ref{fig:topelecdependexposure}), the frequency of storm-related flood
events in this inland county results in a very high expected physical exposure
among this subpopulation, while this county is not included in the top ten
counties for physical exposure based on most of the other exposure metrics.

@@

To assist with future tropical cyclone studies, we created and published open
source software to accompany this article~\citep{hurricaneexposuredata,
hurricaneexposure}. Many previous studies have used geographical
information system software (e.g., ArcGIS) to assess exposure to tropical
cyclones in the \ac{US}~\citep{grabich2016, zandbergen2009, czajkowski2011,
kruk2010}. Here, we offer methods to map and output historic exposure to
tropical cyclones that does not require the use of proprietary software but
instead uses a package written in the R statistical programming
language~\citep{R}, which is free and open-source.

In addition to providing tropical cyclone exposure metrics for individual
hazards, this software and data also allow users to create tropical cyclone
exposure profiles based on multiple hazards or craft exposure indices that
combine hazard metrics~\citep{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones
often act synergistically in causing impacts~\citep{smith2009}. Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.

In creating this hurricane exposure dataset, we aimed for data that are
reliable, available for all eastern \ac{US} counties, and have no missing data
within available dates. Further, we have investigated how well these data
correspond with data from other available sources (Figures~S7\,--\,11). While
generally in agreement with data from other sources, there are a few
limitations. The wind data are based on modeled, rather than observed, values,
and while the modeled wind data generally agree well with post-analysis maximum
wind radii from \ac{HURDAT2}~\citep{landsea2013} (Figure~S7), for a few
tropical cyclones it did not (e.g., Figure~S10). The rainfall data are from
re-analysis data, which are generally well-correlated with observed
ground-based station data but sometimes oversmooth extreme measurements
(Figure~S8).  The flood and tornado data came from the \ac{NOAA} Storm Events
database, which, while a widely-used database of events maintained by
\ac{NOAA}, is based on reports, and so may be prone to
underreporting~\citep{Ashley2008flood, Curran2000}, especially in less
populated areas~\citep{Witt1998, Ashley2007}, as well as to other reporting
errors. While these are important limitations, we selected these data sources
as among the best currently available for measuring each of these hazards at a
multi-county, multi-year scale.

@@

Previous research has highlighted the range of impacts that tropical cyclones
can have in \ac{US} communities. However, studies have varied widely in how they
assess exposure to tropical cyclones for exposure, health impact, and other
impact studies, in some cases using distance to the tropical cyclone's track as
a surrogate metric of exposure to a tropical cyclone's hazards. Here we found
large differences in which counties are exposed to different hazards of
tropical cyclones and that distance is, at best, a moderate, and often a very
poor, surrogate for exposure to the specific tropical cyclone hazards of high
wind, extreme rainfall, flooding, and tornadoes. Use of distance as a surrogate
for any of these hazards could lead to exposure misclassification and, in the
case of tropical cyclone risk and impact studies, including epidemiological
studies, result in biased estimates.  Similarly, if such studies disagree on
their findings, it could result from the often poor agreement between exposure
classifications based on these different metrics, making studies that use
different metrics hard to compare or combine in meta-analyses. Our findings
highlight the importance of clarifying the potential pathway from tropical
cyclone hazards to health impacts when conducting tropical cyclone
epidemiological studies and basing exposure assessment on measurements of these
hazards. To help with this, we provide extensive tropical cyclone
hazard-related measurements for a large collection of historical Atlantic-basin
cyclones, aggregated at the county level to align with the spatial scale at
which much health-related data is collected.

### 2019-01-27 writing/ehp_figures.tex
Rearrange content

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly}
\caption{Counties classified as exposed to Hurricane Ivan (2004) under each
exposure metric (Table 1). The red line shows the track of Hurricane Ivan 
based on the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}).
Similar maps for other large-extent storms are given in Fig. S3.}
\label{fig:ivanexposure} 
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap} 
\caption{Heatmap of Jaccard index values for
specific exposure metric pairs within storms. Only storms between 1996 and 2011,
and for which at least 250 counties were exposed based on at least one metric,
are included. The color of each cell within the main heatmap indicates the value
of the Jaccard index (proportion of counties classified as exposed by both
metrics out of storms classified as exposed by either metric) for a given pair
of metrics for a given storm. Storms are displayed within clusters that have
similar patterns in county-level exposure agreement for metric pairs, based on
hierarchical clustering using the complete link method
\cite{murtagh2012algorithms} (i.e., storms in the same cluster tend to have
similar patterns for the pairwise strength of agreement among metrics); columns
are also ordered based on hierarchical clustering. The colors to the right of
the main heatmap for each storm indicate the total number of counties classified
as exposed to the storm by any of the five metrics, providing an estimate of
storm extent. Maps are available showing the counties identified as exposed
under each of five metrics for the widest-extent storm in each cluster:
Hurricane Ivan (2004) (Fig. \ref{fig:ivanexposure}) and Hurricanes Floyd (1999),
Lee (2011), Cindy (2005), and Katrina (2005) (Fig. S3).} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly} 
\caption{Average number of storm exposures per decade in U.S. counties for 
each exposure metric. The criteria behind each of the five metrics is given 
in Table \ref{tab:exposuremetrics}. The years used to estimate these averages 
are based on years of available exposure data (distance and wind: 1988--2015; 
rain: 1988--2011; flood and tornado: 1996--2015). Similar patterns persist when
analysis is restricted to years with all exposure data available (1996--2011;
Fig. S5).} 
\label{fig:averageexposure} 
\end{figure}

>>>>

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly.pdf}
\caption{Counties classified as exposed to Hurricane Ivan (2004) under each
exposure metric (Table~1). The red line shows the track of Hurricane Ivan 
based on the revised Atlantic hurricane database \ac{HURDAT2}~\citep{landsea2013}.
Similar maps for other large-extent storms are given in Figure~S3.}
\label{fig:ivanexposure} 
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Heatmap of Jaccard index values for specific exposure metric pairs
within storms. Only storms between~1996 and~2011, and for which at least~250
counties were exposed based on at least one metric, are included. The color of
each cell within the main heatmap indicates the value of the Jaccard index
(proportion of counties classified as exposed by both metrics out of storms
classified as exposed by either metric) for a given pair of metrics for a given
storm. Storms are displayed within clusters that have similar patterns in
county-level exposure agreement for metric pairs, based on hierarchical
clustering using the complete link method~\citep{murtagh2012algorithms} (i.e.,
storms in the same cluster tend to have similar patterns for the pairwise
strength of agreement among metrics); columns are also ordered based on
hierarchical clustering. The colors to the right of the main heatmap for each
storm indicate the total number of counties classified as exposed to the storm
by any of the five metrics, providing an estimate of storm extent. Maps are
available showing the counties identified as exposed under each of five metrics
for the widest-extent storm in each cluster: Hurricane Ivan (2004)
(Figure~\ref{fig:ivanexposure}) and Hurricanes Floyd (1999), Lee (2011), Cindy
(2005), and Katrina (2005) (Figure~S3).} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly.pdf} 
\caption{Average number of storm exposures per decade in U.S. counties for each
exposure metric. The criteria behind each of the five metrics is given in Table
\ref{tab:exposuremetrics}. The years used to estimate these averages are based
on years of available exposure data (distance and wind:~1988\,--\,2015; rain:
1988\,--\,2011; flood and tornado:~1996\,--\,2015). Similar patterns persist when
analysis is restricted to years with all exposure data available (1996\,--\,2011;
Figure~S5).} 
\label{fig:averageexposure} 
\end{figure}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Counties with the highest estimated physical exposure among
electricity-dependent Medicare beneficiaries exposed to storms per year in U.S.
counties for each exposure metric. The criteria behind each of the five metrics
are given in Table~1 [use ref] and details of the physical exposure
calculation are given in the Methods. The color of each bar indicates the
number of Medicare beneficiaries in the county reliant on electricity-dependent
medical and assistive equipment as of July~2017~\citep{empower}. The length of
each bar shows the average expected number of these electricity-dependent
Medicare beneficiaries exposed to tropical storms per year based on a given
exposure metric.}
\label{fig:topelecdependexposure}
\end{figure*}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{windcomparison}
\caption{Comparison of estimated wind categories from modeled sustained wind
speed (as used for the wind exposure metric in the main
text;~\citep{stormwindmodel}) versus sustained wind speed determined from the
revised Atlantic hurricane database \ac{HURDAT2}~\citep{landsea2013}. In
\ac{HURDAT2}, wind radii were available for study storms from~2004\,--\,2015
and gives estimates of the maximum radii to which storm winds of 34~\si{\knot},
50~\si{\knot}, and 64~\si{\knot} extended in each four quadrant of the storm at
each of the 6-\si{\hour} storm track observations. We interpolated this data
to~15-\si{\minute} increments and assessed a county as exposed to winds at or above
one of these cutoffs if its population mean center was within~85\% of the
maximum radius for that wind speed in its quadrant of the storm. For each
county in each of the available storms, we also calculated the modeled wind
speed~\citep{stormwindmodel} and then categorized this value into the same
categories available for the \ac{HURDAT2} wind radii ($<$34~\si{\knot};
34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}). Each
point in this graph shows, for a storm, the percent of counties in which the
wind category ($<$34~\si{\knot}; 34\,--\,49.9~\si{\knot};
50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) was the same based on both modeled
winds and the \ac{HURDAT2} wind radii. Only storms with at least one county
with sustained wind of~$\ge$34 \si{\knot}, based on the \ac{HURDAT2} wind
radii, are shown. Hurricanes Sandy (2012) and Ike (2008) were he two storms
with the worst agreement between these two sets of wind data; maps with further
comparisons between the two data sources for these two storms are given in
Figure~\ref{fig:windexamples}.}
\label{fig:windcomparison}
\end{figure}

\begin{figure}[tbhp!] \centering
\includegraphics[width=0.9\linewidth]{raincomparison} \caption{Comparison of
county-level rain exposure based on the reanalysis data used for exposure
assessment in this study \ac{NLDAS-2}~\citep{rui2013nldas,
alhamdan2014environmental} and ground-based weather
stations~\citep{menne2012overview, rnoaa, countyweather}. Each small graph
shows a sample county, and each point on the graph represents a tropical storm
that came within~500 \si{\kilo\metre} of the population mean center of the county.
The x-axis shows the estimated cumulative rainfall (in millimeters) from two
days before to one day after the storm's closest approach to the county based
on the county-aggregated \ac{NLDAS-2} recipitation data used to measure rain
exposure in our main analysis. The ground-based observations (y-axis) are based
on collecting precipitation data from available weather stations in the county,
1988\,--\,2011, summed over the same period from two days before to one day
after the storm's closest approach for each available station. These cumulative
station-based precipitation totals were then averaged across all available
stations in the county to create a county-wide estimate of cumulative
storm-related precipitation for each storm in the county. Horizontal and
vertical lines show the threshold used to classify a storm as exposed based on
cumulative rainfall; storms in the lower left and upper right quadrants are
classified the same regardless of whether reanalysis or station-based
precipitation data is considered, while storms in the upper left and lower
right quadrants would be classified differently. The number of storms within
each county and the average number of stations reporting rainfall during the
county's storms are given above each plot. Note that x- and y-axis ranges
differ by county. An estimate of the rank correlation
(Spearman's~$\rho$~\citep{spearman1904proof}) between measurements from the two
rain data sources is also shown on each graph.} \label{fig:raincomparison}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{floodcomparison}
\caption{Comparison of for a sample of study counties of flood status, based on
NOAA Storm Events listings~\citep{stormevents, noaastormevents}, with total
streamflows at county streamflow gages during tropical storms~\citep{usgsgages,
countyfloods, dataRetrieval}. Each panel represents a separate county. For each
county, we first identified all streamflow gages in the county that had
complete data for Jan.~1~1996\,--\,Dec.~31,~2015. The number of streamflow
gages meeting this criterion are given in parentheses beside the county's name
in the panel title. This analysis covered tropical storm that came
within~500~\si{\kilo\metre} of each sample county between~1996 and~2015. In the
graphs, each point represents a single tropical storm, and the point's position
along the x-axis shows the highest daily total streamflow (cubic feet /
second), summed across all identified streamgages in the county, for a five-day
window centered on the day of the storm's closest approach to the county. The
y-axis separates storms for which a flood event was reported in NOAA's Storm
Events database for the county with a start date within the five-day window of
the storm's closest approach to the county~\citep{stormevents,
noaastormevents}. Boxplots are added to show the distribution of the total
streamflow measurements across storms in the county for storms grouped by
whether or not they were linked with a flood event based on the NOAA Storm
Events data. The color of each point gives the percent of streamflow gages in
the county with a daily streamflow that exceeded a threshold of flooding (the
streamgage's median value for annual peak flow~\citep{countyfloods}) on any day
during the five-day window.  Note that the x-axis scales differ by county,
depending on the number of streamflow gages and typical flow rates for each
gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}
